30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-14 paper.tex
Anonymity
Forgot a4wide package
Sort current systems by date

% setting paragraph indent
\setlength{\parskip}{\baselineskip}

@@

	\subsection{Gnutella}
		Gnutella is a decentralized peer-to-peer network used for distributed search of files. Since the network is fully decentralized, peers in the network are called 'servents', a combination of the words servers and clients. Each peer can act both as a server, answering queries, or as a client, requesting and executing search queries. In order for a client to bootstrap, a new peer connects to one of several known hosts that are almost always available. These peers can be found on http://gnutellahosts.com. Once the peer has joined, there are several messages a servant can send out:

@@

	\subsection{Freenet}
		In Freenet, each data item is represented by a key that is independent of the location of the file. Freenet is called a loosely structured network because of this. To issue a query, the request is passed from client to client where each client makes a decision about the location to send the request next.

@@

	\subsection{NISAN}
		NISAN, or Network Information Service for Anonymization Networks \cite{panchenko2006nisan}, is an anonymization network which implements a distributed node discovery. Not only does a central node administrator (the Directory Server in Tor) imply trust in those servers, Panchenko et al. also argue that a central node administration (the Directory Server in Tor) does not scale, as the current directory server protocol was already improved two times to reduce bandwidth costs, with a fairly low amount of users.

	\subsection{MorphMix}
		MorphMix \cite{rennhard2002introducing} functions similar to both Tor and MIX networks. It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication. Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.

@@

	\subsection{Tribler}
		Information about Tribler.

	\subsection{Tapestry}
		Tapestry is based on the Plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position. A property of Tapestry is that it offers load distribution and routing locality.

	\subsection{Pastry}
		Pastry is very similar to Tapestry, but there are some small differences. One of these differences is the handling of network locality and data object replication. Plastry also uses the Plaxton mesh data structure for the routing algorithm. Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space. Each node can be found in about log(n) steps.

	\subsection{Tarzan}
		Tarzan [TARZAN PAPER] is a fully distributed peer-to-peer anonymity network. It implements a network address translator (NAT) to bridge between nodes running Tarzan and the internet. This means that services don\'t have to be aware of the fact they are running through Tarzan.

@@

	\subsection{Torsk}
		Torsk [TORSKKKK PAPER] is an extension to Tor, designed to be an interoperable replacement for the circuit creation and Directory Service as used by Tor. The authors argue that the current Directory Service does not scale, with the percentage of the traffic in a network dedicated to node discovery growing as the number of nodes grow. With the 2009 version of Tor, they argue that 100\% of the networks traffic would consist of node discovery traffic with roughly 1.2 million clients.

@@

	\begin{itemize}
		\item{Compatibility with Tor:} If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
		\item{Public implementation:} For each network we will explain whether a public implementation is available.
		\item{Used in practice:} Is the network used in practice?
		\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
		\item{Anonimity:} Does the network hide the identities of the sender and/or receiver?
	\end{itemize}

>>>>

% setting paragraph indent
% \setlength{\parskip}{\baselineskip}

@@

	\subsection{Gnutella} % ~2000
		Gnutella is a decentralized peer-to-peer network used for distributed search of files. Since the network is fully decentralized, peers in the network are called 'servents', a combination of the words servers and clients. Each peer can act both as a server, answering queries, or as a client, requesting and executing search queries. In order for a client to bootstrap, a new peer connects to one of several known hosts that are almost always available. These peers can be found on http://gnutellahosts.com. Once the peer has joined, there are several messages a servant can send out:

@@

	\subsection{Freenet} % 2001
		In Freenet, each data item is represented by a key that is independent of the location of the file. Freenet is called a loosely structured network because of this. To issue a query, the request is passed from client to client where each client makes a decision about the location to send the request next.

@@

	\subsection{Tapestry} % 2001
		Tapestry is based on the Plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position. A property of Tapestry is that it offers load distribution and routing locality.

	\subsection{Pastry} % 2001
		Pastry is very similar to Tapestry, but there are some small differences. One of these differences is the handling of network locality and data object replication. Plastry also uses the Plaxton mesh data structure for the routing algorithm. Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space. Each node can be found in about log(n) steps.

	\subsection{MorphMix} % 2002
		MorphMix \cite{rennhard2002introducing} functions similar to both Tor and MIX networks. It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication. Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.

@@

	\subsection{Tarzan} % 2002
		Tarzan [TARZAN PAPER] is a fully distributed peer-to-peer anonymity network. It implements a network address translator (NAT) to bridge between nodes running Tarzan and the internet. This means that services don\'t have to be aware of the fact they are running through Tarzan.

@@

	\subsection{Tribler} % 2008
		Information about Tribler.

	\subsection{NISAN} % 2009
		NISAN, or Network Information Service for Anonymization Networks \cite{panchenko2006nisan}, is an anonymization network which implements a distributed node discovery. Not only does a central node administrator (the Directory Server in Tor) imply trust in those servers, Panchenko et al. also argue that a central node administration (the Directory Server in Tor) does not scale, as the current directory server protocol was already improved two times to reduce bandwidth costs, with a fairly low amount of users.

	\subsection{Torsk} % 2009
		Torsk [TORSKKKK PAPER] is an extension to Tor, designed to be an interoperable replacement for the circuit creation and Directory Service as used by Tor. The authors argue that the current Directory Service does not scale, with the percentage of the traffic in a network dedicated to node discovery growing as the number of nodes grow. With the 2009 version of Tor, they argue that 100\% of the networks traffic would consist of node discovery traffic with roughly 1.2 million clients.

@@

	\begin{itemize}
		\item{Compatibility with Tor:} If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
		\item{Public implementation:} For each network we will explain whether a public implementation is available.
		\item{Used in practice:} Is the network used in practice?
		\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
		\item{Anonymity:} Does the network hide the identities of the sender and/or receiver?
	\end{itemize}
